Making Q-learning robust to time discretization

### 2019-01-17 paper/icml_drau/relatedworks.tex

Here on the other hand we focus on generic RL algorithms that can handle
both discrete and continuous time and space, without collapsing in
continuous time, thus being robust to arbitrary timesteps.

>>>>

Here on the other hand we focus on generic deep RL algorithms that can handle
both discrete and continuous time and space, without collapsing in
continuous time, thus being robust to arbitrary timesteps.
